localhierarchy

### 2025-11-21 README.Rmd
clean up before release

The article on this website presents a practical introduction to the package for the applied user and illustrates the package’s functionality through examples for national and subnational estimation.

@@

See vignette and article.

>>>>

The article on this website presents a practical introduction to the package for the applied user and illustrates the package’s functionality through examples for national estimation.

@@

See article.

## Citation

Please cite as follows:

```{r}
citation("localhierarchy")
```
